
#Exploring Kobe's Shots
###Alexandru Papiu

This is a quick look at the dataset and some of the features. Sports!

Loading in the data:
```{r, message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)

data <- read.csv("data.csv", stringsAsFactors = FALSE)

train <- data[!is.na(data$shot_made_flag),]
test <- data[is.na(data$shot_made_flag),]

train$shot_made_flag <- as.factor(train$shot_made_flag)
```

We have quite a few features in this data set: 
```{r}
names(train)
```

I am curious about two things to begin with: the location of the shots on the court and how Kobe's accuracy is related to certain factors. Let's make two functions, one called `pplot` that plots the accuracy by factor levels and another called `courtplot` that maps features by position.

```{r}

train$shot_made_flag <- factor(train$shot_made_flag, levels = c("1", "0"))

#a plot to see accuracy by feature
pplot <- function(feat) {
    feat <- substitute(feat)
    ggplot(data = train, aes_q(x = feat)) +
        geom_bar(aes(fill = shot_made_flag), stat = "count", position = "fill") +
    scale_fill_brewer(palette = "Set1", direction = -1) +
     ggtitle(paste("accuracy by", feat))

}

# a plot to see position by feature
courtplot <- function(feat) {
        feat <- substitute(feat)
    train %>% 
    ggplot(aes(x = loc_x, y = loc_y)) +
        geom_point(aes_q(color = feat), alpha = 0.9, size = 0.5) +
        ylim(c(-50, 800)) +
        scale_color_brewer(type='div', palette = 'Set2') +
        theme_void() +
        ggtitle(paste(feat))
}
```

Let's take a look at the locations for the various shot_types.
```{r, warning = FALSE}
courtplot(combined_shot_type) #hard to see here.
```
```{r}
courtplot(shot_zone_area)
courtplot(shot_zone_basic)
courtplot(shot_zone_range)
courtplot(shot_type)
```
